---
title: "Analyzing Business Relations & Documents"
subtitle: "Spatial Statistics"
author: "Prof. Dr. Jörg Schoder"
institute: "FFHS" 
date: "`r Sys.Date()`"
bibliography: ../../lit/my_bib.bib
reference-section-title: Quellenverzeichnis
output:
  xaringan::moon_reader:
    self_contained: true
    css: 
         - default
         - ../../css/ffhs-theme_js.css
         - xaringan-themer.css
    includes:
      after_body: ../../css/insert-logo.html
    lib_dir: ../../libs
    nature:
      slideNumberFormat: "%current%/%total%"
      highlightStyle: github
      highlightLines: true
      countIncrementalSlides: false
    seal: false
    

    
---
class: title-slide

```{r xaringan-themer, include=FALSE}
library(xaringanthemer)
style_xaringan(text_color = "#d50006",inverse_text_color = "#FFFFFF",inverse_background_color = "#d50006", title_slide_background_color = "#d50006",header_background_color = "#d50006",header_color = "#FFFFFF",header_h1_font_size = "32px",
  header_h2_font_size = "26px",link_color="#502479",
  header_h3_font_size = "20px",text_slide_number_color = "#d50006",text_slide_number_font_size = "0.5em")
```

```{r xaringanExtra, echo=FALSE}
xaringanExtra::use_progress_bar(color = "#d50006", location = "bottom")
xaringanExtra::use_xaringan_extra(c("tile_view","scribble","panelset","tachyons"))
xaringanExtra::style_panelset_tabs(font_family = "inherit")
#xaringanExtra::use_search(show_icon = TRUE)
#weitere: "share_again","animate_css", "webcam","freezeframe","clipboard","fit_screen","extra-styles" 
xaringanExtra::use_editable(expires = 1)
xaringanExtra::use_freezeframe(trigger = "hover")
``` 

```{r setup, include=FALSE}
options(htmltools.dir.version = FALSE)
library(latex2exp)
library(fontawesome)
library(emo)
source(xfun::from_root("lit","helper.R"))
library(RefManageR)
BibOptions(check.entries = FALSE, 
           bib.style = "authoryear", 
           style = "markdown",
           dashed = TRUE)
file.name <- system.file("Bib", 
                         "my_bib.bib", 
                         package = "RefManageR")
bib <- ReadBib(xfun::from_root("lit","my_bib.bib"))
```

# ER018 - Analyzing Business Relations & Documents

## PVA3

### Räumliche Statistik

 

<br>
<br>
<br>
<br>
<br>
<br>
<br>
### FS 2024
<br>
### Prof. Dr. Jörg Schoder
.mycontacts[
`r fa('github')` @FFHS-EconomicResearch
`r fa('linkedin')` @jfschoder
]


---
layout: true

<div class="my-footer"></div>       

<div style="position: absolute;left:400px;bottom:10px;font-size:9px">`r fa('creative-commons')``r rmarkdown::metadata$author`</div>


---
name: agenda
class: left

.blockquote[Agenda]

## Einführung in die Netzwerkanalayse

* Motivation und Einordnung

* Vermessung von Netzwerken
 




---
class: inverse, center, middle


## Motivation und Einordnung


.blockquote[Statistische Einheiten und Beziehungen]


.blockquote[
"Network analysis (NA) is a set of **integrated techniques to depict relations** among actors and to analyze the social structures that emerge from the recurrence of these relations. The basic assumption is that **better explanations of social phenomena** are yielded by analysis of the relations among entities. This analysis is conducted by collecting **relational data** organized in matrix form. If actors are depicted as nodes, and their relations as lines among pairs of nodes, the concept of social network changes from being a metaphor to an operative analytical tool which utilizes the mathematical language of graph theory and of matrix and relational algebra."
.tr[
`r Citet(bib, "chiesi_network_2001")`

]
]



---
class: left


## Netzwerkanalyse

.blockquote[
"NA can be regarded as a set of techniques with a shared methodological perspective, rather than as a new paradigm in the social sciences. NA techniques allow researchers to specify empirical indicators and to control field hypotheses through the definition and measurement of traditional catch-all concepts like social structure and cohesion."
.tr[
`r Citet(bib, "chiesi_network_2001")`

]
]


???

Network analysis (NA) is a set of integrated techniques to depict relations among actors and to analyze the social structures that emerge from the recurrence of these relations. The basic assumption is that better explanations of social phenomena are yielded by analysis of the relations among entities. This analysis is conducted by collecting relational data organized in matrix form. If actors are depicted as nodes, and their relations as lines among pairs of nodes, the concept of social network changes from being a metaphor to an operative analytical tool which utilizes the mathematical language of graph theory and of matrix and relational algebra. Although deterministic approaches usually emphasise that NA enables study of how the social structure of relationships around a person, group, or organization affects behaviors and attitudes, structurally bounded purposive actions may affect the social structure and vice versa. NA can be regarded as a set of techniques with a shared methodological perspective, rather than as a new paradigm in the social sciences. NA techniques allow researchers to specify empirical indicators and to control field hypotheses through the definition and measurement of traditional catch-all concepts like social structure and cohesion.




---
class: left

.blockquote[Intro R-Objekte]

## R als objektorientierte Sprache

* Objekte lassen sich in Klassen einteilen
  * tibbles, data.frames
  * Vektoren
  * Funktionen



```{r}
library(DiagrammeR)
l=DiagrammeR::mermaid("
graph LR;
A((Orange)) --> B((Grey));

classDef orange fill:#f96;
classDef grey fill:#d3d3d3;
class A orange;
class B grey;
")

widgetframe::frameWidget(l)
```

---
class: left

## ungerichtet

```{r}
library(igraph)
df <- read.table(sep=" ", header=TRUE, text="
Col1 Col2
Ego Alter")
require(igraph)
plot(graph.edgelist(as.matrix(df)))
```



---
class: left

.blockquot[]

## Egonetzwerke

```{r}
library(DiagrammeR)
l=DiagrammeR::mermaid("
graph TB;
A((Orange)) --> B((Grey));

classDef orange fill:#f96;
classDef grey fill:#d3d3d3;
class A orange;
class B grey;
")

widgetframe::frameWidget(l)
```


???

* Fokus auf einer Entität bzw. einem Knoten ("Ego")

---
class: inverse,center,middle

# Wir brauchen eine Pause.

---

background-image: url("http://bit.ly/cs631-donkey")
background-size: 80%





---
class: left

## Quellenverzeichnis

.ref-slide[
```{r, results='asis', echo=FALSE, warning=FALSE}
PrintBibliography(bib)
```
]
